conmat: generate synthetic contact matrices for a given age population

### 2024-06-10 paper/paper.Rmd
Partial dependency plots, test

```{r}
#| label: setup
#| echo: false
#| message: false
#| warning: false
#| comment: false
knitr::opts_chunk$set(comment = "#>",
                      echo = TRUE,
                      out.width = "95%",
                      retina = 3,
                      fig.height = 4,
                      fig.align = "center",
                      dpi = 300,
                      dev = "png")
options(tinytex.clean = FALSE)
```

@@

```{r}
#| label: load-conmat
library(conmat)
perth <- abs_age_lga("Perth (C)")
perth
```

@@

```{r}
#| label: extrapolate-polymod
#| echo: true
perth_contact <- extrapolate_polymod(population = perth)
perth_contact
```

@@

```{r}
#| label: autoplot-contacts
autoplot(perth_contact)
```

@@

The six key features of the relationship are shown in the figure below

@@

>>>>

```{r Document Setup}
#| label: setup
#| echo: false
#| message: false
#| warning: false
#| comment: false
knitr::opts_chunk$set(comment = "#>",
                      echo = TRUE,
                      out.width = "95%",
                      retina = 3,
                      fig.height = 4,
                      fig.align = "center",
                      dpi = 300,
                      dev = "png")
options(tinytex.clean = FALSE)
```

@@

```{r load conmat}
#| label: load-conmat
library(conmat)
perth <- abs_age_lga("Perth (C)")
perth
```

@@

```{r extrapolate polymod}
#| label: extrapolate-polymod
#| echo: true
perth_contact <- extrapolate_polymod(population = perth)
perth_contact
```

@@

```{r autoplot contacts}
#| label: autoplot-contacts
autoplot(perth_contact)
```

@@

The six terms are

The six key features of the relationship are shown in the figure below.

@@

[#TODO notes-to-self: the model structure wasn't generated through any particularly robust process, it was just coming up with structures that looked mildly appropriate for our use case. ]
